AWIPEV-CO2

### 2022-03-30 presentation_old/awipev-CO2_pres_2022-03-31.Rmd

---
title: "AWIPEV-CO2"
subtitle: "First time-series of carbonate chemistry in the Arctic"
author: "Jean-Pierre Gattuso"
date: '`r format(Sys.Date(), "%d %B %Y")`'
#output: slidy_presentation
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    self_contained: FALSE
    seal: FALSE
---

@@

Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
library(widgetframe)
# # install http://phantomjs.org/download.html
# library(webshot)
# # remotes::install_github(c('rstudio/pagedown', 'yihui/xaringan'))
# library(pagedown)

@@

fig_nums <- captioner()
table_nums <- captioner(prefix = "Table")

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

>>>>

---
title: "AWIPEV-CO2"
subtitle: "High frequency time-series of carbonate chemistry in the Arctic"
author: "Jean-Pierre Gattuso"
date: '`r format(Sys.Date(), "%d %B %Y")`'
#output: slidy_presentation
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    self_contained: FALSE
    seal: FALSE
---

@@

Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
#library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
#library(seismicRoll)
if (!require("scales")) install.packages("scales")
library(scales)
#library(widgetframe)
# # install http://phantomjs.org/download.html
# library(webshot)
# # remotes::install_github(c('rstudio/pagedown', 'yihui/xaringan'))
# library(pagedown)

@@

# fig_nums <- captioner()
# table_nums <- captioner(prefix = "Table")

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
